\documentclass{article}

\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\title{Purdue Amateur Radio Club Constitution}
\author{Prepared By: The Officers of Purdue Amateur Radio Club}
\date{December 6, 2024}
% \vspace*{\fill}

% TODO: add provisions about what duties not specified can be done by the
% officers without a vote

\begin{document}

\maketitle \vspace{3ex}

\tableofcontents
\newpage

\setcounter{section}{-1}
\section{Preamble}

We, the members of Purdue Amateur Radio Club, declare this constitution the
legal document of Purdue Amateur Radio Club. Members of the club shall abide by
the following articles. This document shall become effective once approved by
the membership and the Student Activities and Organizations office; from that
time on, it will replace the previous constitution and all other documents of
this nature.

\section{Name}

The official name of this organization is Purdue Amateur Radio Club. The club is
also known by its Federal-Communications-Commission-assigned callsign W9YB.

\section{Purpose}

The purpose of this club is to serve as a means of maintaining an amateur radio
station for the benefit of its members, to promote goodwill among Purdue amateur
radio operators, to serve as a means of social contact for its members, and to
extend the knowledge and art of amateur radio.

\section{Membership}

\subsection{Eligibility}

Membership and participation are free from discrimination on the basis of race,
religion, color, sex, age, national origin or ancestry, genetic information,
marital status, parental status, sexual orientation, gender identity or
expression, disability, or status as a veteran. All people are eligible for
membership of the club.

Pursuant to the Purdue ``Policy Against Hazing,'' Purdue Amateur Radio Club does
not engage in hazing activities of any kind.

\subsection{Requests}

Membership requests can be made to the treasurer during a regular meeting
or---in special circumstances and by consensus of the officers---outside a
meeting. The treasurer of the club shall accept all requests for membership if
the requisite dues have been received. Requests made during a meeting shall be
granted unless an objection to the person becoming a member has been received
from at least two members. The officers shall only disclose who the objectors
are to non-officers during deliberations on accepting the membership request. If
such objections are received, the matter of accepting the membership request
will be put to vote at the next opportunity. Requests made outside of a meeting
and approved by all officers shall be put to a vote at the next opportunity.

\subsection{Dues}

Membership dues for each available membership duration shall be prescribed by
vote during elections at the end of the prior academic year. At this time, the
club may also adopt a list of people exempt from dues for the following year.
People may also be added to the list by vote.

If the fee for a two-semester membership is increased at the end of an academic
year, members who purchased a two-semester membership during the spring term
will owe dues equal to one-half of the increase in order to be considered
current once the third regular meeting of the fall semester begins.

\subsection{Duration}

Membership terms are the current semester or the current and next semesters.
Only the fall and spring semesters are considered. The term of membership
continues until the third regular meeting of the semester after the last
semester of the membership in order to provide a period to renew.

\subsection{Types}

\subsubsection{Members}

A member is any person whose term of membership from their most recent
application has not expired and who is current in any payments due to the club.

\subsubsection{Full Members}

Full members are members who are currently Purdue University students
(undergraduate or graduate) at any Purdue University campus and currently hold a
Federal Communications Commission Amateur Radio License. During breaks between
fall and spring semesters, people who were students during the most recent fall
or spring term shall continue to be considered students.

\subsubsection{Community Members}

Community members are members who are not Purdue University students, but hold a
valid Federal Communications Commission Amateur Radio License.

\subsubsection{Associate Members}

Associate members are members who are not full members or community members.

\subsection{Removal}

Members can be removed with approval from at least two-thirds of the entire body
of voting members. Any member can introduce a proposal to remove a member during
a meeting.

\section{Station}

\subsection{Location}

The club station shall be located in the west tower of the Purdue Memorial
Union.

\subsection{Admission}

Independent ability to unlock the station door by those entitled to access will
be allowed whenever possible through a system maintained by the officers with
any necessary approvals from Purdue Memorial Union building management. Full
members and community members will be allowed access unless their access is
revoked by unanimous vote of club officers. The trustee, the advisor, and anyone
authorized by the Purdue Memorial Union to enter the station space will always
have access. No other people shall be allowed unsupervised access.

Anyone with access to any codes needed to gain access to the station shall guard
them appropriately to ensure they are not disclosed. Codes will be changed if
needed when someone loses access privileges (via revocation or expiration of
membership) to effectuate the change and at any other time the officers consider
it necessary.

If the officers revoke a member's access they can reinstate it at any time by
consensus. Access can also be reinstated by a vote.

People who do not have independent access to the station are permitted to visit
the station as long as someone who has independent access is present and willing
to supervise them.

\subsection{Operation}

All club members are charged with ensuring club property is respected and radio
equipment in club spaces is not used contrary to Federal Communications
Commission regulations or good amateur practice. Operation of the station must
at no time reflect in a detrimental manner on Purdue University. Proper safety
precautions shall be taken at all times in club spaces.

Other rules regarding station operation, conduct within station premises, and
use of club property or station equipment can be adopted by vote.

\subsection{Club Property}

Club property will not be removed from the station premises without approval
through a mechanism adopted by the club. Club equipment must be returned unless
another disposition is approved by a two-thirds vote.

\subsection{Personal Property}

People who bring personal property into the club space accept all responsibility
for loss, damage, and theft. They also must follow all rules adopted by the club
for personal property. In the event removal is provided for by the rules, at
least one week will be given to remove the property, unless it may pose a
hazard.

\section{Meetings}

Meetings consist of regular meetings as well as other meetings. Any powers or
duties not otherwise delegated by the constitution will fall to the membership.
Any of these powers or duties can be delegated to an individual, an office or
functionary position, or a committee. The rules for voting on motions utilizing
these privileges or exercising these duties, for delegating them, and for
forming committees shall be based on the adopted rules of order for the club.

\subsection{Regular Meetings}

Regular meetings are held weekly during the fall and spring semesters except on
days when classes are not in session. The day of the week and time of the
meetings shall be promulgated by the officers at the beginning of each semester.
Official club announcements, such as for elections, and club business requiring
a vote can only be conducted when a quorum is present.

\subsection{Other Meetings}

Other meetings can be called to order anytime a quorum is present to handle
business needing attention. These meetings can occur in person or digitally.

\subsection{Rules}

Rules of order and other rules about how meetings are conducted can be adopted
by two-thirds vote, including provisions for closing a meeting to any groups not
including voting members. At the beginning of each annual officer term any rules
adopted under this section are removed, and until such time as other rules are
adopted, the club shall use Robert's Rules of Order Revised, Fourth Edition.

\subsection{Voting Members}

Voting members are full members who have been present at one of the prior four
regular meetings or the current meeting if one is in session.

\subsection{Quorum}

A quorum shall be at least two-thirds of voting members and at least one
officer. If all officer positions are vacant, an officer shall not be required
for a quorum, and a presiding officer shall be appointed from the present voting
members by vote.

\subsection{Votes}

A quorum must be present for any vote during a meeting. Unless otherwise
specified, votes will pass if more than half of members present vote in
favor---exactly half will not pass. When the fraction is specified, only the
exact fraction is needed to pass.

\section{Officers and Functionaries}

The club officers shall consist of the president, vice president, treasurer, and
secretary. Officers must be full members, and a person may only hold one officer
role.

The club functionaries are the advisor and the trustee. The advisor must be an
employee of Purdue University, they must not be a student of Purdue University,
and they must meet any other requirements under Purdue University student
organization rules for a club advisor. The trustee must meet all applicable
Federal Communications Commission rules for a club license trustee. One person
can hold both roles.

If an officer or functionary stops meeting their eligibility criteria their
position will be immediately vacated.

The president, treasurer, and functionaries are mandatory positions. Officers
and functionaries can vacate, their position either immediately or when an
election to replace them is complete, at their option, by notifying the
officers.

\subsection{Term}

The annual officer term will begin at the last regular meeting in the spring
semester, but not before the spring re-election of all officer positions is
complete. The term will last until the next annual officer term begins.

\subsection{Miscellaneous Duties}

This section specifies duties of officers in addition to duties assigned to them
by other parts of this document. Officers and functionaries are permitted to
delegate their duties as they see fit with the consent of the officers, but the
delegator is still responsible for the duty being discharged in a timely and
correct manner.

\subsubsection{President}

The president shall serve as chief executive officer of the club and preside
over meetings. The president shall organize members and facilitate the club's
mission, strategic plan, and activities. The president shall ensure the smooth
and collegial operation of the club. The president is responsible for the
re-registration of the club with Purdue University as needed. The president will
perform the duties of the secretary if the position is vacant.

\subsubsection{Vice President}

The vice president will assist the president in the leadership and operations of
the club. The vice president will preside in the absence of the president.

\subsubsection{Treasurer}

The treasurer is responsible for maintaining the budget, reporting club fund
balances to full members at meetings if requested, maintaining the roster of
club members, depositing organization funds, and making reimbursements or
expenditures as allowed under this document in a manner approved by the Business
Office for Student Organizations. The treasurer will preside in the absence of
the president and vice president.

\subsubsection{Secretary}

The secretary is responsible for keeping meeting minutes, doing club publicity,
disseminating information about elections, announcing meetings as needed, and
tracking attendance at meetings to maintain the roster of voting members. The
secretary shall provide a mechanism for attendance to be tracked at regular
meetings in their absence. The secretary will preside in the absence of the
president, vice president, and treasurer.

\subsubsection{Advisor}

The advisor will provide advice and suggestions regarding club operations. The
advisor is responsible for signing necessary Purdue University forms for student
organizations and overseeing that operation of the club proceeds in a manner
that complies with Purdue University rules.

\subsubsection{Trustee}

The trustee is responsible for liaising with the Federal Communications
Commission including to maintain the club license(s) and is responsible for the
operation of the station and its equipment. The station license shall be in the
name of the trustee.

\subsection{Elections}

The election process for all positions will begin in the spring semester at a
time selected by the officers. The time shall be selected so that the elections
will be complete by the fifteenth of April if a quorum exists at every regular
meeting from the start of the process until the election. The newly-elected
positions will begin their term when the next annual officer term starts.

The election process shall begin immediately if any mandatory positions are
vacant. The election process for other vacant positions may be started at any
time by unanimous vote of the officers. Officers elected to vacant positions in
these special election shall begin their term immediately, and their term will
last until the end of the current annual officer term.

\subsubsection{Election Process}

When the election process begins, it will be announced at each regular meeting
until the election occurs. Once the announcement is made at a meeting where a
quorum exists, the next regular meeting where a quorum exists shall be the
election.

Members may nominate themselves or others for any position being elected to,
including for multiple positions, but people who object to being nominated shall
not be included. Nominations and objections can be communicated to any of the
officers. Nominations are accepted from the beginning of the election process
until after the last call for nominations at the beginning of the meeting that
is the election. All people nominated for a position that do not object and that
are eligible shall be included on each ballot.

Ballots will be private and ranked choice, but can be in any form approved by
all officers. Elections for functionaries will occur before officers. Elections
will be decided by the ranked pairs method, also known as the Tideman method.
Ties will be broken by the presiding officer.

The elections for officers shall be conducted in the following order: president,
treasurer, secretary, vice president. For the elections of secretary and vice
president, an option ``none'' will be included on the ballot, and if this option
is elected the positions shall be left vacant. If an officer position is left
vacant after any election, any remaining officer positions will be left vacant
and the elections will end. Once a candidate has been selected to an officer
position they will be eliminated from the ballots of the remaining officer
elections, in concert with the order elections are conducted this ensures
members running for multiple positions are voted on for the most critical
positions first.

\subsection{Removal}

Officers or functionaries can be removed, or the election process can be
initiated to replace them, with approval from at least two-thirds of the entire
body of voting members. Any member can introduce a proposal to remove an officer
during a meeting.

\section{Committees and Leadership Positions}

The officers---by consensus---may appoint members to positions of leadership to
execute delegated tasks. The term of appointments shall not extend beyond the
end of the current annual officer term. By consensus the officers can remove
appointments. Appointment does grant officer privileges. All appointed positions
report to the officers.

\section{Budget}

The budgetary year for the club shall be the annual officer term, with the
exception of the first budgetary year after this constitution is adopted, which
shall begin on the day this constitution goes into effect and last until the end
of the annual officer term. The club budget comprises a number of separate
funds. The officer discretionary fund shall be three-quarters of the dues
received during the current budgetary year minus any money spent from the fund.
The general fund shall be four-fifths of any money not from dues or grants
received during the current budgetary year minus any money spent from the fund.
The reserve fund shall be all other available club funds not received from
grants. Grant money applied for and received shall be managed in its own fund
for each grant; each grant fund will be the money from the relevant grant minus
money spent from it.

Money is considered received when it is turned over to the club, not when it is
pledged to the club. Money shall be considered spent and unavailable for future
expenditures as soon as its spending is approved unless the approval is
retracted by vote and the money has not been spent. Money that will be used for
upcoming reimbursements cannot be re-spent.

All club spending shall be done in compliance with all Purdue University rules
for student organizations as well as any restrictions placed on the money by the
donor for grants and donations.

\subsection{Spending Proposals}

To be considered, the effect of spending proposals on club funds must be
documented. This can be done by including a section in the proposal from the
treasurer detailing the effect of the proposal, as long as it is current at the
time of voting on the proposal. Alternatively, if the treasurer is in attendance
when the proposal is introduced and voted on, the treasurer can report the
effect on the balance of club funds at such times. The treasurer shall prepare
this section or make this report for any spending proposal submitted to them or
considered during a meeting they are present at. Proposals cannot be considered
if they spend money not currently available in the funds they propose spending
from.

\subsection{Officer Discretionary Fund}

Money from the officer discretionary fund can be spent for the benefit of the
club by consensus of the officers as they see fit, without approval from the
club membership.

\subsection{General Fund}

Money from the general fund can be spent by vote during a meeting or by approval
of more than half of the entire body of voting members. Proposals to spend money
from the general fund can be introduced by any member during a meeting. Outside
of meetings, by consensus of the officers, a proposal can be introduced to
voting members to seek approval by more than half of them.

\subsection{Reserve Fund}

Money from the reserve fund can only be spent as approved by two-thirds vote.
Proposals to spend money from the reserve fund can only be introduced by at
least half of officers during a meeting. Other members do not have standing to
propose spending from the reserve fund, and should instead submit their proposal
to the officers.

\subsection{Grant Funds}

Each grant applied for and received has its own fund. Spending from these funds
shall be approved in the same manner as the general fund. If a grant proposal
prepared by the officers will designate received money for a specific purpose,
it is tantamount to spending the money for that purpose, so such grant proposals
must be approved in the same way as grant fund spending before being submitted.

\section{Constitutional Amendments}

Proposals to amend or replace the constitution can be submitted to the
membership by any member during a regular meeting if a quorum is present. The
proposed amendment will require approval from at least three-quarters of voting
members to be accepted. Proposals not reaching the required level of support by
the end of the semester they are submitted in will be rejected.

The secretary shall submit any approved amendment to the Purdue University
Office of Student Activities and Organizations. The amendment will not go into
effect unless and until it is approved by this office.

\subsection{Dissolution}

The club can only be dissolved via a constitutional amendment. Proposals for
constitutional amendments that effectuate a dissolution shall provide for the
disposition of club property and funds.

% \newpage

% \section*{Approvals}

% \vspace{4ex}

% \subsection*{Members}

% \begin{minipage}{0.3\textwidth}
%     \begin{itemize}
%         \item Member 1
%         \item Member 2
%         \item Member 3
%         \item Member 4
%     \end{itemize}
% \end{minipage}
% \hfill
% \begin{minipage}{0.3\textwidth}
%     \begin{itemize}
%         \item Member 5
%         \item Member 6
%         \item Member 7
%         \item Member 8
%     \end{itemize}
% \end{minipage}
% \hfill
% \begin{minipage}{0.3\textwidth}
%     \begin{itemize}
%         \item Member 9
%         \item Member 10
%         \item Member 11
%         \item Member 12
%     \end{itemize}
% \end{minipage}

% \vspace{6ex}

% \subsection*{Officers and Officials}

% \vspace{10ex}

% \begin{tabular}{@{}p{3.5in}@{}}
% \hrulefill \\
% Robert J Sammelson \\
% President of Purdue Amateur Radio Club \\
% \end{tabular}

% \vspace{8ex}

% \noindent
% \begin{tabular}{@{}p{3.5in}@{}}
% \hrulefill \\
% Wrigley A Starkweather \\
% Treasurer of Purdue Amateur Radio Club \\
% \end{tabular}

% \vspace{8ex}

% \noindent
% \begin{tabular}{@{}p{3.5in}@{}}
% \hrulefill \\
% Owen M Stevens \\
% Secretary of Purdue Amateur Radio Club \\
% \end{tabular}

% \vspace{8ex}

% \noindent
% \begin{tabular}{@{}p{3.5in}@{}}
% \hrulefill \\
% Dr. Andrew Robison \\
% Advisor to Purdue Amateur Radio Club \\
% \end{tabular}

% \vspace{8ex}

% \noindent
% \begin{tabular}{@{}p{3.5in}@{}}
% \hrulefill \\
% Purdue Student Activities and Organizations Office \\
% \end{tabular}

\end{document}
